Backpropagating Gravitational wave events

### 2022-05-24 src/ms.tex
adding in PB citations

\section{Introduction}
As the detection rate of gravitation waves (GWs) from merging
double-compact-object (DCO) binaries increases with the sensitivity of the
ground-based GW detector network
\citep{Abbott2018,LIGOScientificCollaboration2015,Buikema2020,Tse2019,Acernese2015,Acernese2019,Aso2013,Akutsu2021},
we are beginning to constrain the astrophysical processes which shape the
evolution of GW progenitor populations. One of the most common ways to study
progenitor populations of GW mergers is through population synthesis simulations
for a host of formation environments. In the case of isolated binary evolution, merging 
double compact objects can form from massive binary stars through the
standard stable mass transfer or common envelope channels 
\citep[e.g.][]{Belczynski2002, Dominik2012, Belczynski2016, Zevin2020, Bavera2021, Broekgaarden2021, VanSon2022} 
as well as through chemically homogenous evolution \citep{Mandel2016, Marchant2016, deMink2016} 
or with population III stars \citep[e.g.][]{Belczynski2004, Kinugawa2014, Inayoshi2016, Inayoshi2017, Tanikawa2021, Tanikawa2022}.
Merging DCO binaries can also originate from a wide variety of dynamically active environments including 
triple (or higher multiple) systems \citep[e.g. ][]{Antonini2017, Silsbee2017, Fragione2019, VignaGomez2021}, 
as well as young stellar clusters \citep[e.g.][]{Ziosi2014, Banerjee2017, DiCarlo2020, Chattopadhyay2022}, 
globular clusters \citep[e.g.][]{PortegiesZwart2000, OLeary2006, Downing2010, Samsing2014, Rodriguez2015, Rodriguez2016, Askar2017, Rodriguez2019}, 
nuclear star clusters \citep[][]{Miller2009, Antonini2016}, or a mix of all three \citep[e.g.][]{Mapelli2022}.
Finally, more exotic channels like active galactic nuclei which combine both gravitational and gas interactions 
\citep[e.g.][]{McKernan2018, McKernan2020, Secunda2020, Ford2021} or primordial black hole formation \textbf{KB add these citations} can lead 
to merging DCOs observable with a ground-based detector network. For a discussion of the relative rates of each 
formation envrionment and channels within, see \citet{Mandel2022}. Traditionally in these studies, the
population is studied through a Monte-Carlo approach.  Using theoretically
motivated distributions of initial parameters (age, metallicity, masses, orbital
separations, eccentricities, etc), initial populations are evolved with fixed
astrophysical assumptions (population synthesis parameter settings) to produce a
synthetic catalog of mergers which can be compared to observations from
GW detectors.

>>>>

\section{Introduction}
As the detection rate of gravitation waves (GWs) from merging
double-compact-object (DCO) binaries increases with the sensitivity of the
ground-based GW detector network
\citep{Abbott2018,LIGOScientificCollaboration2015,Buikema2020,Tse2019,Acernese2015,Acernese2019,Aso2013,Akutsu2021},
we are beginning to constrain the astrophysical processes which shape the
evolution of GW progenitor populations. One of the most common ways to study
progenitor populations of GW mergers is through population synthesis simulations
for a host of formation environments. In the case of isolated binary evolution, merging 
double compact objects can form from massive binary stars through the
standard stable mass transfer or common envelope channels 
\citep[e.g.][]{Belczynski2002, Dominik2012, Belczynski2016, Zevin2020, Bavera2021, Broekgaarden2021, VanSon2022} 
as well as through chemically homogenous evolution \citep{Mandel2016, Marchant2016, deMink2016} 
or with population III stars \citep[e.g.][]{Belczynski2004, Kinugawa2014, Inayoshi2016, Inayoshi2017, Tanikawa2021, Tanikawa2022}.
Merging DCO binaries can also originate from a wide variety of dynamically active environments including 
triple (or higher multiple) systems \citep[e.g.][]{Antonini2017, Silsbee2017, Fragione2019, VignaGomez2021}, 
as well as young stellar clusters \citep[e.g.][]{Ziosi2014, Banerjee2017, DiCarlo2020, Chattopadhyay2022}, 
globular clusters \citep[e.g.][]{PortegiesZwart2000, OLeary2006, Downing2010, Samsing2014, Rodriguez2015, Rodriguez2016, Askar2017, Rodriguez2019}, 
nuclear star clusters \citep[][]{Miller2009, Antonini2016}, or a mix of all three \citep[e.g.][]{Mapelli2022}.
Finally, more exotic channels like active galactic nuclei which combine both gravitational and gas interactions 
\citep[e.g.][]{McKernan2018, McKernan2020, Secunda2020, Ford2021} or primordial black holes \citep[e.g.][]{Bird2016, AliHaimoud2017} can lead 
to merging DCOs observable with a ground-based detector network. For a discussion of the relative rates of each 
formation envrionment and channels within, see \citet{Mandel2022}. Traditionally in these studies, the
population is studied through a Monte-Carlo approach.  Using theoretically
motivated distributions of initial parameters (age, metallicity, masses, orbital
separations, eccentricities, etc), initial populations are evolved with fixed
astrophysical assumptions (population synthesis parameter settings) to produce a
synthetic catalog of mergers which can be compared to observations from
GW detectors.
